\documentclass[10pt]{beamer}
% \documentclass[aspectratio=169, 10pt]{beamer} % For wider width
\usepackage[]{ocean}
\usepackage{ngntrgduc}


% Preamble ---------------------------------------------------------------
\title[Ocean Beamer Theme]{\huge Ocean Beamer Theme}
\author[ngntrgduc]{\large Trung-Duc Nguyen}
\institute[HCMUS]{
  \inst{}
  \large University of Science - VNUHCM \\Faculty of Mathematics and Computer Science\\
}
\date{\today}


% Start ---------------------------------------------------------------
\begin{document}

\begin{frame}[plain] % [Plain] hide headline and footline of the first slide
    \maketitle 
\end{frame}

\begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[subsectionstyle=hide]
\end{frame}

\section{First section}
\subsection{Enumerate}
\begin{frame}
    \frametitle{Enumerate}
    \begin{enumerate}
        \item Sample 1.
        \item Sample 2.
            \begin{enumerate}
                \item Sample 1.
                    \begin{enumerate}
                        \item Sample 1.
                        \item Sample 2.
                    \end{enumerate}
                \item Sample 2.
            \end{enumerate}
    \end{enumerate}
\end{frame}

\subsection{Itemize}
\begin{frame}{Itemize}
    \begin{itemize}
        \item Item 1.
        \item Item 2.
            \begin{itemize}
                \item Subitem 1.
                    \begin{itemize}
                        \item Subsubitem 1.
                        \item Subsubitem 2.
                    \end{itemize}
                \item Subitem 2.
            \end{itemize}
    \end{itemize}
\end{frame}

\section{Second section}
\subsection{Block}
\begin{frame}
    \frametitle{Block}
    \begin{block}{Normal block}
        Normal box.
    \end{block} 
        
    \begin{alertblock}{Alert}
        Alert box.
    \end{alertblock}
        
    \begin{examples}
        Example box.
    \end{examples}
\end{frame}
    
\subsection{Two-column slide}
\begin{frame}
    \frametitle{Two-column slide}
    \begin{columns}
    \column{0.5\textwidth}
    This is a text in first column. \[  e^{i\pi} + 1 = 0 \]
        \begin{itemize}
            \item First item in first column.
            \item Second item in first column.
        \end{itemize}
    
    \column{0.5\textwidth}
    This is a text in second column. \\
    This is another text in second column. 
    \end{columns}
\end{frame}

\section{Third section}
\subsection{First subsection}
\begin{frame}{First subsection}
    \alert{This text highlighted} because it's \color{ocean}{important.}
\end{frame}

\section{Fourth section}
\subsection{First subsection}
\begin{frame}{First subsection}
    First subsection
\end{frame}

\subsection{Second subsection}
\begin{frame}{Second subsection}
    Second subsection
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
        \item Conclusion 1
        \item Conclusion 2
    \end{itemize}
\end{frame}

\begin{frame}[plain]
    \begin{tikzpicture}[overlay, remember picture]
        \node[anchor=center] at (current page.center) {
            \Huge \textcolor{ocean}{Q \& A}
        };
    \end{tikzpicture}
\end{frame}

\begin{frame}[plain]
    \begin{tikzpicture}[overlay, remember picture]
        \node[anchor=center] at (current page.center) {
            \Huge \textcolor{ocean}{Thank You}
        };
    \end{tikzpicture}
\end{frame}

\begin{frame}{References}
    \begin{itemize}
        \item References 1
        \item References 2
    \end{itemize}
\end{frame}

\end{document}